Efficient pedigree recording for fast population genetics simulation

### 2017-12-27 forwards_paper.tex
clarify units

To measure the performance gains from recording the pedigree we ran simulations both with and without recording.
All simulations implemented a discrete-time Wright-Fisher population of diploid
population size $N$, simulated for $10N$ generations.
The simulations without pedigree recording introduced neutral mutations at a rate
equal to the recombination rate,
so $\mu = r$, where $\mu$ and $r$ are the expected number of mutations and recombinations,
respectively, per gamete and per generation.
% Both mutations and recombinations occur as Poisson processes with respective means $\mu$ and $r$,
% and we used the infinitely-many sites mutation model \citep{Kimura1969-uc}.
We ran simulations with different values of $N$
and of the \emph{scaled} parameter $\rho = 4Nr$,
categorized by the value of $\rho$, since this
is what most strongly determines run time
(along with the scaled mutation rate, $\theta = 4N\mu$, which is also equal to $\rho$.)

>>>>

To measure the performance gains from recording the pedigree we ran simulations both with and without recording.
All simulations implemented a discrete-time Wright-Fisher population of diploid
population size $N$, simulated for $10N$ generations.
The simulations without pedigree recording introduced neutral mutations at a rate
equal to the recombination rate,
so $\mu = r$, where $\mu$ and $r$ are the expected number of mutations per gamete and recombination breakpoints per
diploid,
respectively, each generation. 
% Both mutations and recombinations occur as Poisson processes with respective means $\mu$ and $r$,
% and we used the infinitely-many sites mutation model \citep{Kimura1969-uc}.
We ran simulations with different values of $N$
and of the \emph{scaled} parameter $\rho = 4Nr$,
categorized by the value of $\rho$, since this
is what most strongly determines run time
(along with the scaled mutation rate, $\theta = 4N\mu$, which is also equal to $\rho$.)
